### 2012-11-18 pretextual.tex
arrumada geral, adentrando texto

	\begin{epigrafebot}
		{from Pantheon import Obatalá\, \, \, \\
                from World import sharing, kitten \\
                \vspace{.1in}
                while True: \; \; \; \; \; \; \; \; \; \; \; \; \; \; \; \,\\
                    if sharing == 0: \; \; \; \; \;  \; \; \; \; \; \\
                        Obatalá.kill( kitten ) \; \; \;}
        {Autoria coletiva e anônima (2010)}
	\end{epigrafebot}

>>>>

	\begin{epigrafebot}
		{from Pantheon import Obatalá\, \, \, \\
                from World import sharing, kitten \\
                \vspace{.1in}
                while True: \; \; \; \; \; \; \; \; \; \; \; \; \; \; \; \,\\
                    if sharing == 0: \; \; \; \; \;  \; \; \; \; \; \\
                        Obatalá.kill( kitten )}
        {Autoria coletiva e anônima (2010)}
	\end{epigrafebot}
